Progress Report

### 2020-07-28 documentation/Optimization Work/07_24_20.tex
Reduced to single paraemter for IRS phases and added corresponding results to a progress report

Using a matched filter  and precoder which satisfies the transmission power constraint gives (normalize each column)
\begin{equation}
\mW = \mathbf{H}_{Total}^H
\end{equation}

Numerical results for $s_k \in \mathcal{NC}(0,1)$, $n_k \in \mathcal{NC}(0,1)$
\begin{itemize}
\item
zf mu: 202.0989509146119
zf std: 57.23864582855936
\item
matched mu: 476.69650954785794
matched std: 239.3529067968275
\end{itemize}

\bibliography{bibliography}

\end{document}

>>>>

The following numerical results evaluate the MSE the channel above with $s_k \in \mathcal{NC}(0,\frac{1}{N_R})$, $n_k \in \mathcal{NC}(0,\frac{1}{N_R})$.
For each channel realization, I evaluate the MSE for the matched filter and zero-forcing filter using $\phase = e^{j\theta}\mI$ for 10 uniform spaced values of $\theta \in [0, 2\pi]$. Then I collect the mean and variance of the 10 MSEs for the channel realization. I repeat and average across 1000 channel realizations. I perform this same analysis across different values of $\rho$ in the exponential correlation model (i.e.  $r_{i,j}=\rho^(i-j)$. The results in Figure \ref{MSE_correlation} indicate that the variance of the MSE over different values of the phase matrix parameter, $\theta$,  can be quite large. In particular when the correlation parameter, $\rho$ is close to 1.
		\begin{figure}[H]
	\includegraphics[width= 15cm,height = 10cm]{figures/over_10_thetas}
	  \caption{Comparison MSE over different amounts of correlation.}
	  	  \label{MSE_correlation}
	\end{figure}

Based on the measurement data collected in \cite{martin2000multiple}, the correlation between antennas can reach $.5$ even in a, $4 \times 4 $ MIMO systems. 
Since the IRS introduces the potential for additional correlation it seems reasonable to allow for $\rho = .5$.

\section{Next Steps: Methods for Phase Optimization}
\begin{enumerate}
\item
	Method from \cite{huang2018achievable}.
\begin{itemize}
\item
	No LOS of correlation
\item
	Requires full CSIT at IRS
\item 
	Assumes a ZF precoder in order to simplify sum-capacity objective function.
\item
	Alternating algorithm approach with two main steps
	\begin{enumerate}
	\item 
		Minimize transmission power w.r.t phases
	\item
		Maximize rate wrt power
	\end{enumerate}
\end{itemize}

\item 
	Method from \cite{huang2018achievable}.

\end{enumerate}
\bibliography{bibliography}
\end{document}
